### 2022-07-13 manuscript.tex
Merge pull request #255 from SORTEE-Github-Hackathon/RCO-moving-tables [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3778b55f2950608f6cb50fc7f2a8a320ce757b6a.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3778b55f2950608f6cb50fc7f2a8a320ce757b6a/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2664445561

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1aab55c67fc728559fe52f3f106965c1eef0e179/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1aab55c67fc728559fe52f3f106965c1eef0e179}{SORTEE-Github-Hackathon/manuscript@1aab55c}
on July 12, 2022.

@@

Beyond supporting collaborative code development, GitHub can be used for writing manuscripts.
Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
Writing a manuscript on GitHub may take more time when compared to using conventional text processors\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
Nevertheless, GitHub has many features that can allow for a powerful collaborative workflow when writing manuscripts.
Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
Co-authors can contribute changes or suggest revisions to a manuscript written in GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 1}).
Relevant literature or issues can be made using the Discussions and Issues features.
Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms (\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents).

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3778b55f2950608f6cb50fc7f2a8a320ce757b6a/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3778b55f2950608f6cb50fc7f2a8a320ce757b6a}{SORTEE-Github-Hackathon/manuscript@3778b55}
on July 13, 2022.

@@

Beyond supporting collaborative code development, GitHub can be used for writing manuscripts.
Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
Writing a manuscript on GitHub may take more time when compared to using conventional text processors\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
Nevertheless, GitHub has many features that can allow for a powerful collaborative workflow when writing manuscripts.
Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
Co-authors can contribute changes or suggest revisions to a manuscript written in GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 2}).
Relevant literature or issues can be made using the Discussions and Issues features.
Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms (\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents).
